An Expressive and Efficient Solution to the Service Selection Problem

### 2010-06-29 publicaciones/iswc10/paperISWC10-v3.tex
dos typos mas en paperISWC10-v3

As it is shown below, LAV descriptions are achieved with mappings
that define the services as conjunctive queries involving the generic
concepts in the ontology. Thus, every time that a service changes or
a new one becomes available, only a tiny fraction of the mappings
must be updated, usually just one mapping.
Likewise, user requests can be modeled as conjunctive queries over the
generic concepts in a way that the SSP can be cast as the problem
of rewriting a query in terms of a set of views, the so-called Query
Rewriting Problem (QRP) that is well-known in the area of data
integration~\cite{Chen05,JaudoinPRST05}, query optimization and data
maintenance~\cite{AfratiLU07,levy:bucket}, and for which several
scalable approaches had been
proposed~\cite{arvelo:aaai06,pods:DuschkaG97,sac:DuschkaG97,levy:bucket,pottinger:minicon}.
Furthermore, users' preferences and constraints on the set of the
selected services to serve a given request are supported by the
adoption of a simple yet expressive language for preferences. 
These preferences and constraints further refine and rank the
the set of valid rewritings of the posed query, in a way that
the best solution to the SSP corresponds to the best-ranked 
valid rewritings of the corresponding QRP.

@@

The preliminary experiments show that the approach can be applied to
real-sized problems. We are currently working on a complete implementation
of the formalism in order to offer its full expressivity.
In the future, we plan to use other off-the-shelf SAT tools such 
as MiniMaxSat that is able to find a best model without the need 
to compile the CNF into d-DNNF.

>>>>

As it is shown below, LAV descriptions are achieved with mappings
that define the services as conjunctive queries involving the generic
concepts in the ontology. Thus, every time that a service changes or
a new one becomes available, only a tiny fraction of the mappings
must be updated, usually just one mapping.
Likewise, user requests can be modeled as conjunctive queries over the
generic concepts in a way that the SSP can be cast as the problem
of rewriting a query in terms of a set of views, the so-called Query
Rewriting Problem (QRP) that is well-known in the area of data
integration~\cite{Chen05,JaudoinPRST05}, query optimization and data
maintenance~\cite{AfratiLU07,levy:bucket}, and for which several
scalable approaches had been
proposed~\cite{arvelo:aaai06,pods:DuschkaG97,sac:DuschkaG97,levy:bucket,pottinger:minicon}.
Furthermore, users' preferences and constraints on the set of the
selected services to serve a given request are supported by the
adoption of a simple yet expressive language for preferences. 
These preferences and constraints further refine and rank 
the set of valid rewritings of the posed query, in a way that
the best solution to the SSP corresponds to the best-ranked 
valid rewritings of the corresponding QRP.

@@

The preliminary experiments show that the approach can be applied to
real-sized problems. We are currently working on a complete implementation
of the formalism in order to offer its full expressiveness.
In the future, we plan to use other off-the-shelf SAT tools such 
as MiniMaxSat that is able to find a best model without the need 
to compile the CNF into d-DNNF.
